Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-16 paper.tex
extra paragraph about pu comparison fig

Also notable is that different modeling choices (e.g. time step duration,
facility discretization, etc.) may have varying levels of significance
depending on the scenario/context they are operating in.  Figure
\ref{fig:puinv-compare} shows the same inventory curves from Figure
\ref{fig:puinv} superimposed.  Before the fuel shortage begins, differences
between each of the four cases are relatively minor.  However, after the
shortage begins around year 100, separated Pu inventories vary much more
significantly between the different cases.

@@

>>>>

Figure \ref{fig:puinv-compare} shows the same inventory curves from Figure
\ref{fig:puinv} superimposed. Counter-intuitively, lower separated plutonium
inventory during the shortage generally indicates fewer unfueled reactors.
Lower inventory levels mean available Pu is being utilized more efficiently
rather than sitting idle.  Cases 3 and 4 with their longer time steps show
higher inventories indicating a more severe shortage.  Post shortage, they
also fall a bit behind on building up Pu stocks due to the delayed
contributions of more unfueled reactors to the separated Pu pool.

@@

Also notable is that different modeling choices (e.g. time step duration,
facility discretization, etc.) may have varying levels of significance
depending on the scenario/context they are operating in.  As shown in Figure
\ref{fig:puinv-compare} Before the fuel shortage begins, differences between
each of the four cases are relatively minor.  However, after the shortage
begins around year 100, separated Pu inventories vary much more significantly
between the different cases.
